Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements

### 2025-04-14 Submission.Rmd
updating paper
Editing the full paper again.

csl               : "apa7.csl"
documentclass     : "apa7" #interact
classoption       : "man"
#output            : "word_document"
output            : papaja::apa6_pdf

---

@@

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes. As an additional contribution, we utilize the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).

## The Challenge-Hindrance Stressor Framework

@cavanaugh2000empirical's challenge-hindrance stressor framework serves as the theoretical foundation for this work. First, *resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [high work pressure, for example, is commonly cited as a demand, e.g., @demerouti2001job]. The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job). 
@cavanaugh2000empirical proposed the challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*. Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge]. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity [@lepine2022challenge].

@@

IS THIS TOO CLOSELY TIED TO THE JOB DEMANDS RESOURCES THEORY? CHECK

The second set of predictions focus on associations with theory-relevant outcomes of the challenge-hindrance stressor-frameworks [@cavanaugh2000empirical]. The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta]. We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. See Figure \@ref(fig:ourmodel) for proposed associations. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, @hakanen2008job found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement [e.g., @schaufeli2017applying].

@@

AGAIN, CHECK TO SEE IF THIS IS TOO CLOSELY ALIGNED WITH JDR RATHER THAN CHALLENGE-HINDRANCE

@@

@@

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table 1 provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance. We would expect to see minimal correlations if job characteristics *were* uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.

@@

papaja::apa_table(regtable, 
              caption = "Moderated regression summary of outcomes regressed on challenges and resources",
              escape=FALSE,
              note="* = p < .05; ** = p < .01")
```

@@

papaja::apa_table(regtable,
                 caption = "Moderated regression summary of outcomes regressed on hindrances and resources",
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01")
```
### Hindrances, Resources, and Outcomes

@@

#running it with unstandardized bs here. 
cr_eng_m3u <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, modreg)
#summary(cr_eng_m3u)

cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge_center, modx = overall.resource_center, interval = FALSE,
              int.width = 0.8, x.label = "Challenge", legend.main = "Resource", y.label = "Engagement")
cr_eng_plot
```

@@

hr_stress_m3u <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, modreg)
#summary(hr_stress_m3u)

hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
              int.width = 0.8, x.label = "Hindrance", legend.main = "Resource", y.label = "Stress")
hr_stress_plot
```

@@

hr_burn_m3u <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, modreg)
#summary(hr_burn_m3u)

hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
              int.width = 0.8, x.label = "Hindrance", legend.main = "Resource", y.label = "Burnout")
hr_burn_plot
```

@@

In addition to the above findings, this paper made several additional important contributions. We utilized a diverse sample of employees across industries who responded to common O\*Net items. While O\*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of demands and resources. Further, we provide a repository for other researchers with listing of O\*Net demands and resources across activity and context items for the benefit of all future researchers. We also explored not only context and activity holistically, but at a higher level aggregation, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work dimensions, as well as the relationships among them.

@@

>>>>

csl               : "apa7.csl"
documentclass     : "apa7" #interact
classoption       : "man"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex 
---

@@

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes. As an additional contribution, we utilize the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).

## Theoretical Foundations

The job demands-resources theory (e.g., Bakker & Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes. Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001). Demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [high work pressure, for example, is commonly cited as a demand, e.g., @demerouti2001job]. The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).

@cavanaugh2000empirical proposed the challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*. Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge]. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity [@lepine2022challenge].

@@

he second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- @bakker2017job and challenge-hindrance stressor-frameworks @cavanaugh2000empirical. Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta]. We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. See Figure \@ref(fig:ourmodel) for proposed associations. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, @hakanen2008job found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement [e.g., @schaufeli2017applying].

@@

@@

```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*Net occupational categories (previous was across 84 O/*Net items - this is across 568 individual workers).", fig.height=10}

## Job classifications

workers <- read.csv("workers.csv")             ## Probably need to revisit our coding - 10/14/22

# ggplot(workers, aes(O.Net.Job.Family.Categories))+
#   geom_histogram(stat="count") + coord_flip()

## Combining categories

workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Transportation and Material Moving"] <- "Physical Labor"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Protective Service"] <- "Physical Labor"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Production"] <- "Physical Labor"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Personal Care and Service"] <- "Physical Labor"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Installation Maintenance and Repair"] <- "Physical Labor"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Food Preparation and Serving Related"] <- "Physical Labor"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Farming Fishing and Forestry"] <- "Physical Labor"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Construction and Extraction"] <- "Physical Labor"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Building and Grounds Cleaning and Maintenance"] <- "Physical Labor"

## with Alicia 12/1
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Architecture and Engineering"] <- "Computer & Engineering"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Computer and Mathematical"] <- "Computer & Engineering"

workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Life Physical and Social Science"] <- "Education, Science & Health"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Educational Instruction and Library"] <- "Education, Science & Health"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Practitioner and Technical"] <- "Education, Science & Health"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Community and Social Service"] <- "Education, Science & Health"

workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Office and Administrative Support"] <- "Admin, Healthcare & Legal"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Legal"] <- "Admin, Healthcare & Legal"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Support"] <- "Admin, Healthcare & Legal"

workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Arts Design Entertainment Sports Media"] <- "Other"
workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Military Specific"] <- "Other"

#3 in plot all categories, combined and standalone

#ggplot(workers, aes(O.Net.Job.Family.Categories)) +
#  geom_histogram(stat="count") + coord_flip()

forworkers2 <- anova[,c(2:85)]
dataworker <- cbind(forworkers2,workers$O.Net.Job.Family.Categories)    ## to repeat O*Net analyses
                                     ## This gets worker info into convergence file

dataworker$overall <- rowMeans(dataworker[1:84], na.rm=TRUE)

names(dataworker)[names(dataworker) == 'workers$O.Net.Job.Family.Categories'] <- 'JobFamily'

ggplot(dataworker, aes(x=overall)) + geom_histogram() + facet_wrap(~JobFamily, nrow=8)

workeraov <- aov(overall ~ JobFamily, data=dataworker)

library(lsr)  ## for eta squared
effect.size <- etaSquared(workeraov)

@@

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table 1 provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance (i.e., Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)). We would expect to see minimal correlations if job characteristics *were* uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.

@@

papaja::apa_table(regtable, 
              caption = "Moderated regression summary of outcomes regressed on challenges and resources",
              escape=FALSE,
              note="* = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered")
```

@@

papaja::apa_table(regtable,
                 caption = "Moderated regression summary of outcomes regressed on hindrances and resources",
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered")
```
### Hindrances, Resources, and Outcomes

@@

#running it with unstandardized bs here. 
cr_eng_m3u <- lm(engagement ~ overall.challenge + overall.resource + overall.challenge*overall.resource, modreg)
#summary(cr_eng_m3u)

cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge, modx = overall.resource, interval = FALSE,
              int.width = 0.8, x.label = "Challenge", legend.main = "Resource", y.label = "Engagement")
cr_eng_plot
```

@@

hr_stress_m3u <- lm(stress ~ overall.hindrance + overall.resource + overall.hindrance*overall.resource, modreg)
#summary(hr_stress_m3u)

hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance, modx = overall.resource, interval = FALSE, 
              int.width = 0.8, x.label = "Hindrance", legend.main = "Resource", y.label = "Stress")
hr_stress_plot
```

@@

hr_burn_m3u <- lm(burnout ~ overall.hindrance + overall.resource + overall.hindrance*overall.resource, modreg)
#summary(hr_burn_m3u)

hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance, modx = overall.resource, interval = FALSE, 
              int.width = 0.8, x.label = "Hindrance", legend.main = "Resource", y.label = "Burnout")
hr_burn_plot
```

@@

In addition to the above findings, this paper made several additional important contributions. We utilized a diverse sample of employees across industries who responded to common O\*Net items. While O\*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of an extensive range of demands and resources. Further, we provide a repository for other researchers with listing of O\*Net demands and resources across activity and context items for the benefit of all future researchers. We also explored not only context and activity holistically, but at a higher level aggregation, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work dimensions, as well as the relationships among them.

@@

Another interesting avenue for future research is to explore these patterns by job type. @kubicek2023all, for instance, found that employee workload was positively related to strain, and that this relationship was stronger for care and social workers compared to other types of employees. This finding suggests that job type may be an important moderator, and worthy of exploration moving forward.
